### 2021-08-10 00_header/metadata.tex
Optimized PDF metadata

% Dissertation information
\newcommand*{\TheAuthor}{Manuel Schlund}
\newcommand*{\TheColloquiumDate}{2 August 2021}
\newcommand*{\TheDegree}{\foreignlanguage{ngerman}{%
    Doktor der Naturwissenschaften (\Dr{} rer.\@ nat.\@)}%
}
\newcommand*{\TheInstitute}{Institute of Environmental Physics (IUP)}
\newcommand*{\TheKeywords}{%
  Climate Modeling\sep Climate Model Weighting\sep Climate Projections\sep %
  Climate Sensitivity\sep Emergent Constraints\sep Machine Learning%
}
\newcommand*{\TheLanguage}{en-US}
\newcommand*{\TheLicense}{%
  Creative Commons Attribution 4.0 International License%
}
\newcommand*{\TheLicenseURL}{https://creativecommons.org/licenses/by/4.0/}
\newcommand*{\TheMonth}{August 2021}
\newcommand*{\ThePrimaryExaminer}{\Prof{} \Dr{} Veronika Eyring}
\newcommand*{\TheSecondaryExaminer}{\Prof{} \Dr{} Pierre Gentine}
\newcommand*{\TheSubmissionDate}{13 April 2021}
\newcommand*{\TheThesis}{Doctoral Dissertation}
\newcommand*{\TheTitle}{%
  Constraining Uncertainties in Multi-Model Projections of the Future Climate
  with Observations%
}
\newcommand*{\TheUniversity}{University of Bremen}

@@

  dioxide (CO2) concentration, a multimodel mean (MMM) of 3.74 K and a

@@

  CMIP6 ensemble, the CMIP6 models can be used for crosschecking the emergent

@@

  participating in CMIP5 to (171 ± 12) GtC yr−1 , compared to the unconstrained
  model range of 156–247 GtC yr−1 . In a second step, an ML model is used to

>>>>

% Dissertation information
\newcommand*{\TheAuthor}{Manuel Schlund}
\newcommand*{\TheColloquiumDate}{2 August 2021}
\newcommand*{\TheDegree}{\foreignlanguage{ngerman}{%
    Doktor der Naturwissenschaften (\Dr{} rer.\@ nat.\@)}%
}
\newcommand*{\TheInstitute}{Institute of Environmental Physics (IUP)}
\newcommand*{\TheKeywords}{%
  Climate Change\sep Climate Modeling\sep Climate Projections\sep
  Climate Sensitivity\sep Climate Model Weighting\sep Emergent Constraints\sep
  Machine Learning%
}
\newcommand*{\TheLanguage}{en-US}
\newcommand*{\TheLicense}{%
  Creative Commons Attribution 4.0 International License%
}
\newcommand*{\TheLicenseURL}{https://creativecommons.org/licenses/by/4.0/}
\newcommand*{\TheMonth}{August 2021}
\newcommand*{\ThePrimaryExaminer}{\Prof{} \Dr{} Veronika Eyring}
\newcommand*{\TheSecondaryExaminer}{\Prof{} \Dr{} Pierre Gentine}
\newcommand*{\TheSubmissionDate}{13 April 2021}
\newcommand*{\TheThesis}{Doctoral Dissertation}
\newcommand*{\TheTitle}{%
  Constraining Uncertainties in Multi-Model Projections of the Future Climate
  with Observations%
}
\newcommand*{\TheUniversity}{University of Bremen}

@@

  dioxide (CO2) concentration, a multi-model mean (MMM) of 3.74 K and a

@@

  CMIP6 ensemble, the CMIP6 models can be used for cross-checking the emergent

@@

  participating in CMIP5 to (171 ± 12) GtC yr−1, compared to the unconstrained
  model range of 156–247 GtC yr−1. In a second step, an ML model is used to
